\documentclass[a4paper]{report}

\usepackage{color}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[utf8]{inputenc}

% Configure links
\hypersetup{
    colorlinks=true
}

% Macros for class link. Every class has a label with pattern: class:<Class name>
\newcommand{\classlink}[1]{\hyperref[class:#1]{#1}}

% Macros for primitive XML types
\newcommand{\booleantype}{\textbf{boolean}}
\newcommand{\datetype}{\textbf{date}}
\newcommand{\stringtype}{\textbf{string}}

% Style for XML code listings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset {
    basicstyle=\footnotesize,
    columns=fullflexible,
    showstringspaces=false,
    commentstyle=\color{gray}\upshape
}

\lstdefinelanguage{RAKIP} {
    morestring=[b]",
    morestring=[s]{>}{<},
    morecomment=[s]{<?}{?>},
    stringstyle=\color{black},
    identifierstyle=\color{darkblue},
    keywordstyle=\color{cyan},
    morekeywords={xmlns,version,type} % list your attributes here
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Macros for elements tables %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\starttable{%
    \tabular{|l|c|c|c|}
    \hline
    \textbf{Element} & \textbf{Type} & \textbf{Min. Ocurrences} & \textbf{Max. Ocurrences} \\    
    \hline
}
\def\stoptable{%
    \hline \endtabular
}
\def\R #1|#2|#3|#4{ #1&#2&#3&#4 \\}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\chapter{Introduction}

The RAKIP Markup Language (RakML) is an XML-based format for the description of model metadata.

...

\chapter{Technical specification}

\section{Primitive data types}
The primitive data types used in RAKIP-ML are taken from the XML Schema 1.0 including: \stringtype, \booleantype, \textbf{int} and \textbf{date}.

\section{General structure}
Every RAKIP model involves four main metadata components: general information, scope, data background and model math. A RAKIP-ML document has one model with these components.

\section{Common types}

\subsection{Assay}
\label{class:Assay}

\starttable
    \R Name | string | 1 | 1
    \R Description | string | 0 | 1
    \R MoisturePercentage | string | 0 | 1
    \R FatPercentage | string | 0 | 1
    \R DetectionLimit | string | 0 | 1
    \R QuantificationLimit | string | 0 | 1
    \R LeftCensoredData | string | 0 | 1
    \R ContaminationRange | string | 0 | 1
    \R UncertaintyValue | string | 0 | 1
\stoptable

\paragraph{Name}
A name given to the assay.

\paragraph{Description}
General description of the assay. Corresponds to the Protocol REF in ISA.

\paragraph{MoisturePercentage}
Percentage of moisture in the original sample.

\paragraph{FatPercentage}
Percentage of fat in the original sample.

\paragraph{DetectionLimit}
Limit of detection reported in the unit specified by the variable ``Hazard Unit''.

\paragraph{QuantificationLimit}
Limit of quantification reported in the unit specified by the variable ``Hazard Unit''.

\paragraph{LeftCensoredData}
Percentage of measures equal to LOQ and/or LOD.

\paragraph{ContaminationRange}
Range of result of the analytical measure reported in the unit specified by the variable ``Hazard unit''.

\paragraph{UncertaintyValue}
Indicate the expanded uncertainty (usually 95\% confidence interval) value associated with the measurement expressed in the unit reported in the field ``Hazard unit''.

\begin{lstlisting}[caption={Example of Assay}, language=RAKIP]
<Name>Bradford protein assay</Name>
<Description>spectroscopic analytical procedure used to measure
    the concentration of protein in a solution. It is subjective,
    i.e., dependent on the amino acid composition of the
    measured protein.
</Description>
<DetectionLimit>30-300</DetectionLimit>
<QuantificationLimit>5000 - 8000</QuantificationLimit>
<ContaminationRange>500-4000</ContaminationRange>
\end{lstlisting}

\subsection{Contact}
\label{class:Contact}

\starttable
    \R Title | string | 0 | 1
    \R FamilyName | string | 0 | 1
    \R GivenName | string | 0 | 1
    \R Email | string | 1 | 1
    \R Telephone | string | 0 | 1
    \R StreetAddress | string | 0 | 1
    \R Country | string | 0 | 1
    \R City | string | 0 | 1
    \R ZipCode | string | 0 | 1
    \R Region | string | 0 | 1
    \R TimeZone | string | 0 | 1
    \R Gender | string | 0 | 1
    \R Note | string | 0 | 1
    \R Organization | string | 0 | 1
\stoptable

\begin{lstlisting}[language=RAKIP, caption={Example of Contact}]
<Title>Dr.</Title>
<FamilyName>Romanov</FamilyName>
<GivenName>Natalia</GivenName>
<Email>black_widow@marvel.com</Email>
<Telephone>030 12345</Telephone>
<StreetAddress>Nahmitzer Damm 40</StreetAddress>
<Country>Russian Federation</Country>
<City>Berlin</City>
<Region>Berlin-Brandenburg</Region>
<Organization>SHIELD</Organization>
\end{lstlisting}

\subsection{Exposure}
\label{class:Exposure}
\starttable
    \R Type | string | 1 | 1
    \R UncertaintyEstimation | string | 0 | 1
    \R MethodologicalTreatmentOfLeftCensoredData | string | 0 | *
    \R LevelOfContaminationAfterLeftCensoredDataTreatment | string | 0 | *
    \R Scenario | string | 0 | *
\stoptable

\paragraph{Type}
Type of the exposure

\paragraph{UncertaintyEstimation}
Analysis to estimate uncertainty

\paragraph{MethodologicalTreatmentOfLeftCensoredData}
describe the mathematical method to replace left-censored data: recommandation of WHO (2013), distribution or ohters

\paragraph{LevelOfContaminationAfterLeftCensoredDataTreatment}
describe the range of of the level of contamination after left censored data treatment

\paragraph{Scenario}
describe the different scenario of exposure assessment

\subsection{Hazard}
\label{class:Hazard}

\starttable
    \R Type | string | 0 | 1
    \R Name | string | 1 | 1
    \R Description | string | 0 | 1
    \R Unit | string | 0 | 1
    \R AdverseEffect | string | 0 | 1
    \R SourceOfContamination | string | 0 | 1
    \R BenchmarkDose | string | 0 | 1
    \R MaximumResidueLimit | string | 0 | 1
    \R NoObservedAdverseAffectLevel | string | 0 | 1
    \R AcceptableOperatorExposureLevel | string | 0 | 1
    \R AcuteReferenceDose | string | 0 | 1
    \R AcceptableDailyIntake | string | 0 | 1
    \R IndSum | string | 0 | 1
\stoptable

\paragraph{Type}
General classification of the hazard for which the model or data applies.

\paragraph{Name}
Name of the hazard for which the model or data applies.

\paragraph{Description}
Description of the hazard for which the model or data applies.

\paragraph{Unit}
Unit of the hazard for which the model or data applies.

\paragraph{AdverseEffect}
Morbidity, mortality, origin.

\paragraph{SourceOfContamination}
Source of contamination, origin.

\paragraph{BenchmarkDose}
A dose or concentration that produces a predetermined change in response rate of an adverse effect (called the benchmark response or BMR) compared to background.

\paragraph{MaximumResidueLimit}
International regulations and permissible maximum residue levels in food and drinking water.

\paragraph{NoObservedAdverseAffectLevel}
Level of exposure of an organism, found by experiment or observation, at which there is no biologically or statistically significant increase in the frequency or severity of any adverse effects in the exposed population when compared to its appropriate control.

\paragraph{LowestObservedAdverseAffectLevel}
Lowest concentration or amount of a substance found by experiment or observation that causes an adverse alteration of morphology, function, capacity, growth, development, or lifespan of a target organism distinguished from normal organisms of the same species under defined conditions of exposure.

\paragraph{AcceptableOperatorExposureLevel}
Maximum amount of active substance to which the operator may be exposed without any adverse health effects. The AOEL is expressed as milligrams of the chemical per kilogram body weight of the operator.

\paragraph{AcuteReferenceDose}
An estimate (with uncertainty spanning perhaps an order of magnitude) of a daily oral exposure for an acute duration (24 hours or less) to the human population (including sensitive subgroups) that is likely to be without an appreciable risk of deleterious effects during a lifetime.

\paragraph{AcceptableDailyIntake}
Measure of amount of a specific substance in food or in drinking water tahta can be ingested (orally) on a daily basis over a lifetime without an appreciable health risk.

\paragraph{IndSum}
Define if the parameter reported is an individual residue/analyte, a summed residue definition or part of a sum a summed residue definition.

\begin{lstlisting}[language=RAKIP, caption={Example of Hazard}]
<Type>Organic contaminants</Type>
<Name>Norovirus (Norwalk-like virus)</Name>
<Description>norovirus is described as nast and hard to get rid
of</Description>
<Unit>CFU</Unit>
<AdverseEffect>morbitity</AdverseEffect>
<SourceOfContamination>sewage</SourceOfContamination>
<MaximumResidueLimit>0.01 mg/kg</MaximumResidueLimit>
<NoObservedAdverseAffectLevel>10 mg</NoObservedAdverseAffectLevel>
<LowestObservedAdverseAffectLevel>40 mg</LowestObservedAdverseAffectLevel>
<AcceptableOperatorExposureLevel>50 mg</AcceptableOperatorExposureLevel>
<AcuteReferenceDose>80 mg</AcuteReferenceDose>
<AcceptableDailyIntake>20 mg</AcceptableDailyIntake>
\end{lstlisting}

\subsection{Laboratory}
\label{class:Laboratory}

\starttable
    \R Accreditation | string | 0 | 1
    \R Name | string | 0 | 1
    \R Country | string | 0 | 1
\stoptable

\paragraph{Accreditation}
The laboratory accreditation to ISO/IEC 17025.

\paragraph{Name}
Laboratory code (National laboratory code if available) or Laboratory name 

\paragraph{Country}
Country where the laboratory is placed. (ISO 3166-1-alpha-2).

\begin{lstlisting}[language=RAKIP, caption={Example of Laboratory}]
<Accreditation>Accredited</Accreditation>
<Name>National High Magnetic Field Laboratory</Name>
<Country>United States</Country>
\end{lstlisting}   

\subsection{ModelCategory}
\label{class:ModelCategory}

\starttable
    \R ModelClass | string | 1 | 1
    \R ModelSubClass | string | 0 | 1
    \R ModelClassComment | string | 0 | 1
    \R BasicProcess | string | 0 | 1
\stoptable

\paragraph{ModelClass}
Type of model used to build-up the risk assessment structure.

\paragraph{ModelSubClass}
Sub-cassification of the model given the Model Class

\paragraph{BasicProcess}
Defines the impact of the specific process on the hazard

\begin{lstlisting}[language=RAKIP, caption={Example of ModelCategory}]
<ModelClass>Dose-response model</ModelClass>
<ModelClassComment>This Model Class is very special</ModelClassComment>
\end{lstlisting}

\subsection{ModelEquation}
\label{class:ModelEquation}

\starttable
    \R Name | string | 1 | 1
    \R Class | string | 0 | 1
    \R ModelEquation | string | 1 | 1
    \R Reference | string | 1 | 1
    \R ModelHypothesis | string | 0 | *
\stoptable

\paragraph{Name}
A name given to the model equation

\paragraph{Class}
Information on that helps to categorize model equations

\paragraph{ModelEquation}
The pointer to the file that holds the software code (e.g. R-script)

\paragraph{Reference}
Information on the source, where the equation has been extracted from - if available

\subsection{Parameter}
\label{class:Parameter}

\starttable
    \R Id | string | 1 | 1
    \R Classification | string | 1 | 1
    \R Name | string | 1 | 1
    \R Description | string | 0 | 1
    \R Unit | string | 1 | 1
    \R UnitCategory | string | 0 | 1
    \R DataType | string | 0 | 1
    \R Source | string | 0 | 1
    \R Subject | string | 0 | 1
    \R Distribution | string | 0 | 1
    \R Value | string | 0 | 1
    \R Reference | \classlink{Reference} | 0 | *
    \R VariabilitySubject | string | 0 | 1
    \R MinValue | string | 0 | 1
    \R MaxValue | string | 0 | 1
    \R Error | string | 0 | 1
\stoptable

\paragraph{Id}
An unambiguous and sequential ID given to the parameter. To be compatible with SBML, only letters from A to Z, numbers and ``\_'' are acepted for ID creation.

\paragraph{Classification}
General classification of the parameter (e.g. Input, Constant, Output...).

\paragraph{Name}
A name given to the parameter.

\paragraph{Description}
General description of the parameter.

\paragraph{Unit}
Unit of the parameter.

\paragraph{UnitCategory}
General classification of the parameter unit.

\paragraph{DataType}
Information on the data format of the parameter, e.g. if it is a categorial variable, int, double, array of size x,y,z.

\paragraph{Source}
Information on the type of knowledge used to define the parameter value.

\paragraph{Subject}
Scope of the parameter, e.g. if it refers to an animal, a batch of animals, a batch of products, a carcass, a carcass skin etc.

\paragraph{Distribution}
Information on the distribution describing the parameter (e.g. variability, uncertainty, point estimate...) .

\paragraph{Value}
Numerical value of the parameter. A default value is mandatory (needs to be provided) for each of the the ``Input parameters''. If the parameter value is provided in a file, the path of the file needs to be provided.

\paragraph{Reference}
Information on the source, where the value of the parameter has been extracted from - if available. The format should use that used in other ``Reference'' metadata. Preferably DOI.

\paragraph{VariabilitySubject}
Information ``per what'' the variability is described. It can be variability between broiler in a flock,  variability between all meat packages sold in Denmark, variability between days, etc.

\paragraph{MinValue}
Numerical value of the minimum limit of the parameter that determines the range of applicability for which the model applies

\paragraph{MaxValue}
Numerical value of the maximum limit of the parameter that determines the range of applicability for which the model applies

\paragraph{Error}
Error of the parameter value.

\begin{lstlisting}[language=RAKIP, caption={Example of Parameter}]
<Id>Dose_matrix</Id>
<Classification>input</Classification>
<Name>Dose_matrix</Name>
<Description>matrix with GEC NoV for each serving (rows=servings;
    columns = number of different employee-teams that prepare food)
</Description>
<Unit>Others</Unit>
<UnitCategory>Other</UnitCategory>
<DataType>matrixOfNumbers</DataType>
<Source>Article</Source>
<Subject>Animal</Subject>
<Distribution>Bernoulli 1</Distribution>
<Value>as.matrix(read.table(file =\"Dose_matrix.csv\",sep=\",\",
    header = TRUE, row.names=1))</Value>
<VariabilitySubject>days</VariabilitySubject>
<MinValue>10000.0</MinValue>
<MaxValue>0.0</MaxValue>
<Error>0.5</Error>
\end{lstlisting}

\subsection{PopulationGroup}
\label{class:PopulationGroup}

\starttable
    \R Name | string | 1 | 1
    \R TargetPopulation | string | 0 | 1
    \R PopulationSpan | string | 0 | *
    \R PopulationDescription | string | 0 | *
    \R PopulationAge | string | 0 | *
    \R PopulationGender | string | 0 | 1
    \R BMI | string | 0 | *
    \R SpecialDietGroups | string | 0 | *
    \R PatternConsumption | string | 0 | *
    \R Region | string | 0 | *
    \R Country | string | 0 | *
    \R PopulationRiskFactor | string | 0 | *
    \R Season | string | 0 | *
\stoptable

\paragraph{Name}
Name of the population for which the model or data applies

\paragraph{TargetPopulation}
population of individual that we are interested in describing and making statistical inferences about

\paragraph{PopulationSpan}
Temporal information on the exposure duration

\paragraph{PopulationDescription}
Description of the population for which the model applies (demographic and socio-economic characteristics for example). Background information that are needed in the data analysis phase: size of household, education level, employment status, professional category, ethnicity, etc.

\paragraph{PopulationAge}
describe the range of age or group of age

\paragraph{PopulationGender}
describe the percentage of gender

\paragraph{BMI}
describe the range of BMI or class of BMI or BMI mean

\paragraph{SpecialDietGroups}
sub-population with special diets (vegetarians, diabetics, group following special ethnic diets)

\paragraph{PatternConsumption}
describe the consumption of different food items: frequency, portion size

\paragraph{Region}
Spatial information (area) on which the population group of the model or data applies

\paragraph{Country}
Country on which the population group of the model or data applies

\paragraph{PopulationRiskFactor}
population risk factor that may influence the outcomes of the study, confounder should be included

\paragraph{Season}
distribution of surveyed people according to the season (influence consumption pattern)

\begin{lstlisting}[language=RAKIP, caption={Example of PopulationGroup}]
<Name>human consumer, no age specification</Name>
<TargetPopulation>seniors</TargetPopulation>
<PopulationDescription>
    80% are considered susceptible to infection
</PopulationDescription>
<PopulationGender>50% male</PopulationGender>
<BMI>18.5 - 24.9</BMI>
<SpecialDietGroups>love cake</SpecialDietGroups>
<Region>Madrid</Region>
<Country>Spain</Country>
<PopulationRiskFactor>low physical activity</PopulationRiskFactor>
<Season>spring</Season>
\end{lstlisting}

\subsection{QualityMeasures}
\label{class:QualityMeasures}

\starttable
    \R SSE | double | 0 | 1
    \R MSE | double | 0 | 1
    \R RMSE | double | 0 | 1
    \R RSquared | double | 0 | 1
    \R AIC | double | 0 | 1
    \R BIC | double | 0 | 1
\stoptable

\begin{lstlisting}[language=RAKIP, caption={Example of QualityMeasures}]
<SSE>0.0</SSE>
<MSE>0.2</MSE>
<RMSE>0.3</RMSE>
<RSquared>0.9</RSquared>
<AIC>0.0</AIC>
<BIC>1.0</BIC>
\end{lstlisting}

\subsection{Reference}
\label{class:Reference}

\starttable
    \R IsReferenceDescription | boolean | 1 | 1
    \R Type | string | 0 | 1
    \R Date | string | 0 | 1
    \R Pmid | string | 0 | 1
    \R Doi | string | 0 | 1
    \R AuthorList | string | 0 | 1
    \R Title | string | 1 | 1
    \R Abstract | string | 0 | 1
    \R Journal | string | 0 | 1
    \R R Volume | int | 0 | 1
    \R Issue | int | 0 | 1
    \R Status | string | 0 | 1
    \R Website | string | 0 | 1
    \R Comment | string | 0 | 1
\stoptable

\paragraph{IsReferenceDescription}
Indicates whether the publication serves as the reference description for the model.

\begin{table}
    \centering
    \begin{tabular}{l l l l l l l}    
        \hline
        ABST & CHAP & DICT & GEN & MANSCPT & PCOMM & VIDEO \\
        ADVS & CHART & EBOOK & GOVDOC & MAP & RPRT & \\
        AGGR & CLSWK & ECHAP & GRANT & MGZN & SER & \\
        ANCIENT & COMP & EDBOOK & HEAR & MPCT & SLIDE & \\
        ART & CONF & EDJOUR & ICOMM & MULTI & SOUND & \\
        BILL & CPAPER & ELECT & INPR & MUSIC & STAND & \\
        BLOG & CTLG & ENCYC & JOUR & NEW & STAT & \\
        BOOK & DATA & EQUA & JFULL & PAMP & THES & \\
        CASE & DBASE & FIGURE & LEGAL & PAT & UNPB & \\
        \hline
    \end{tabular}
    \caption{Publication types}
    \label{table:publicationtypes}
\end{table}

\paragraph{Type}
Type of the publication. Takes a value from the reserved words listed at \ref{table:publicationtypes}.

\paragraph{Year}
Temporal information on the publication date.

\paragraph{Pmid}
The PubMed ID related to this publication.

\paragraph{Doi}
The DOI related to this publication.

\paragraph{AuthorList}
Name and surname of the authors who contributed to this publication.

\paragraph{Title}
Title of the publication in which the model or the data has been described.

\paragraph{Abstract}
Abstract of the publication in which the model or the data has been described.

\paragraph{Journal}
Publication journal.

\paragraph{Volume}
Publication volume.

\paragraph{Issue}
Publication issue.

\paragraph{Status}
Publication status.

\paragraph{Website}
Publication website.

\paragraph{Comment}
Publication comment.

\begin{lstlisting}[language=RAKIP, caption={Example of Reference}]
<IsReferenceDescription>true</IsReferenceDescription>
<Type>PAMP</Type>
<Date>3805-07-02</Date>
<Doi>10.1111/risa.12758</Doi>
<AuthorList>Jack Bauer, Kiefer Sutherland</AuthorList>
<Title>Quantitative Risk Assessment of Norovirus Transmission in Food Establishments:
    Evaluating the Impact of Intervention Strategies and Food Employee Behavior on
    the Risk Associated with Norovirus in Foods.
</Title>
<Abstract>
    This research looks at the work of Margaret C. Anderson, the editor of the
    Little Review. The review published first works by Sherwood Anderson, James
    Joyce, Wyndham Lewis, and Ezra Pound. This research draws upon mostly primary
    sources including memoirs, published letters, and a complete collection of the
    Little Review. Most prior research on Anderson focuses on her connection to the
    famous writers and personalities that she published and associated with. This
    focus undermines her role as the dominant creative force behind one of the most
    influential little magazines published in the 20th Century. This case example
    shows how little magazine publishing is arguably a literary art.
</Abstract>
<Status>Accepted</Status>
<Website>https://nature.com</Website>
<Comment>publisher demands edits</Comment>
\end{lstlisting}

\subsection{SpatialInformation}
\label{class:SpatialInformation}

\starttable
    \R Region | string | 0 | 1
    \R Country | string | 0 | 1
\stoptable

\paragraph{Region}
Spatial information (area) on which the model or data applies.

\paragraph{Country}
Country on which the model or data applies.

\begin{lstlisting}[language=RAKIP, caption={Example of SpatialInformation}]
<Region>Bayern</Region>
<Country>Germany</Country>
\end{lstlisting}

\subsection{Study}
\label{class:Study}

\starttable
    \R Identifier | string | 0 | 1
    \R Title | string | 1 | 1
    \R Description | string | 0 | 1
    \R DesignType | string | 0 | 1
    \R AssayMeasurementType | string | 0 | 1
    \R AssayTechnologyType | string | 0 | 1
    \R AssayTechnologyPlatform | string | 0 | 1
    \R AcreditationProcedureForTheAssayTechnology | string | 0 | 1
    \R ProtocolName | string | 0 | 1
    \R ProtocolType | string | 0 | 1
    \R ProtocolDescription | string | 0 | 1
    \R ProtocolURI | string | 0 | 1
    \R ProtocolParametersName | string | 0 | 1
    \R ProtocolComponentsName | string | 0 | 1
    \R ProtocolComponentsType | string | 0 | 1
\stoptable

\paragraph{Identifier}
A user defined identifier for the study

\paragraph{Title}
A title for the Study.

\paragraph{Description}
A brief description of the study aims.

\paragraph{DesignType}
The type of study design being employed.

\paragraph{AssayMeasurementType}
The measurement being observed in this assay.

\paragraph{AssayTechnologyType}
The technology being employed to observe this measurement.

\paragraph{AssayTechnologyPlatform}
The technology platform used.

\paragraph{AccreditationProcedureForTheAssayTechnology}
Accreditation procedure for the analytical method used.

\paragraph{ProtocolName}
The name of the protocol, e.g.Extraction Protocol.

\paragraph{ProtocolType}
The type of the protocol, preferably coming from an Ontology, e.g. Extraction Protocol.

\paragraph{ProtocolDescription}
A description of the Protocol.

\paragraph{ProtocolURI}
A URI to link out to a publication, web page, etc. describing the protocol.

\paragraph{ProtocolParametersName}
The parameters used when executing this protocol.

\paragraph{ProtocolComponentsType}
The components used when carrying out this protocol.

\begin{lstlisting}[language=RAKIP, caption={Example of Study}]
<Identifier>Study_Generic_Sheet_1</Identifier>
<Title>Quantitative Risk Assessment of Norovirus Transmission in Food
    Establishments: Evaluating the Impact of Intervention Strategies
    and Food Employee Behavior on the Risk Associated with Norovirus
    in Foods.
</Title>
<Description>This Study will show, wether the FSK Lab will correctly
    read and run a generic and fully annotated model.
</Description>
<DesignType>Trial and Error</DesignType>
<AssayMeasurementType>It works or it doesn't</AssayMeasurementType>
<AssayTechnologyType>Anatomic-pathologic Tests</AssayTechnologyType>
<AssayTechnologyPlatform>Orbital Platform</AssayTechnologyPlatform>
<AccreditationProcedureForTheAssayTechnology>ISO/IEC17025
</AccreditationProcedureForTheAssayTechnology>
<ProtocolName>Extraction Protocol of FSK</ProtocolName>
<ProtocolType>Extraction Protocol</ProtocolType>
<ProtocolDescription>The protocol is definitely not made up</ProtocolDescription>
<ProtocolURI>https://url-for-study-protocol-location.bfr.bund.de</ProtocolURI>
<ProtocolVersion>version 1.0</ProtocolVersion>
<ProtocolParametersName>Parameter 1</ProtocolParametersName>
<ProtocolComponentsName>windows pc</ProtocolComponentsName>
<ProtocolComponentsType>hardware</ProtocolComponentsType>
\end{lstlisting}

\subsection{StudySample}
\label{class:StudySample}

\starttable
    \R SampleName | string | 1 | 1
    \R ProtocolOfSampleCollection | string | 1 | 1
    \R SamplingStrategy | string | 0 | 1
    \R TypeOfSamplingProgram | string | 0 | 1
    \R SamplingMethod | string | 0 | 1
    \R SamplingPlan | string | 1 | 1
    \R SamplingWeight | string | 1 | 1
    \R SamplingSize | string | 1 | 1
    \R LotSizeUnit | string | 0 | 1
    \R SamplingPoint | string | 1 | 1
\stoptable

\paragraph{SampleName}
An unambiguous ID given to the samples used in the assay.

\paragraph{ProtocolOfSampleCollection}
Additional protocol for sample and sample collection. Corresponds to the Protocol REF in ISA.

\paragraph{SamplingStrategy}
Sampling strategy (ref. EUROSTAT - Typology of sampling strategy, version of July 2009).

\paragraph{TypeOfSamplingProgram}
Indicate the type of programm for which the samples have been collected. .

\paragraph{SamplingMethod}
Sampling method used to take the sample.

\paragraph{SamplingPlan}
description of data collection technique: stratified or complex sampling (several stages).

\paragraph{SamplingWeight}
description of the method employed to compute sampling weight (nonresponse-adjusted weight).

\paragraph{SamplingSize}
number of units, full participants, partial participants, eligibles, not eligible, unresolved (eligibility status not resolved)….

\paragraph{LotSizeUnit}
Unit in which the lot size is expressed.

\paragraph{SamplingPoint}
Point in the food chain where the sample was taken. (Doc. ESTAT/F5/ES/155 ``Data dictionary of activities of the establishments'').

\begin{lstlisting}[language=RAKIP, caption={Example of StudySample}]
<SampleName>Sample 1</SampleName>
<ProtocolOfSampleCollection>SampleID_1</ProtocolOfSampleCollection>
<SamplingStrategy>Convenient sampling</SamplingStrategy>
<TypeOfSamplingProgram>Diet study</TypeOfSamplingProgram>
<SamplingMethod>According to Reg 152/2009</SamplingMethod>
<SamplingPlan>Random sampling</SamplingPlan>
<SamplingWeight>description of the method employed to compute sampling
    weight (nonresponse-adjusted weight)
</SamplingWeight>
<SamplingSize>10000.0</SamplingSize>
<LotSizeUnit>log10(CFU/25g)</LotSizeUnit>
<SamplingPoint>Catering</SamplingPoint>
\end{lstlisting}

\chapter{GenericModel}

\section{GeneralInformation}

\starttable
    \R Name | string | 1 | 1
    \R Source | string | 0 | 1
    \R Identifier | string | 1 | 1
    \R Author | \classlink{Contact} | 1 | 1
    \R Creator | \classlink{Contact} | 1 | 1
    \R CreationDate | date | 1 | 1
    \R ModificationDate | date | 0 | *
    \R Rights | string | 1 | 1
    \R Available | string | 0 | 1
    \R Format | string | 0 | 1
    \R Reference | \classlink{Reference} | 1 | *
    \R Language | string | 0 | 1
    \R Software | string | 0 | 1
    \R LanguageWrittenIn | string | 0 | 1
    \R ModelCategory | \classlink{ModelCategory} | 0 | 1
    \R Status | string | 0 | 1
    \R Objective | string | 0 | 1
    \R Description | string | 0 | 1
\stoptable

\paragraph{Name}
Name given to the model or data.

\paragraph{Source}
A related resource from which the described resources is derived.

\paragraph{Identifier}
An unambiguous ID given to the model or data.

\paragraph{Author}
Person who generated the model code or generated the data set originally.

\paragraph{Creator}
The person responsible for creating the model file in the present form or the person responsible for creating the data file in the present form.

\paragraph{CreationDate}
Temporal information on the model creation date.

\paragraph{ModificationDate}
Temporal information on the last modification of the model.

\paragraph{Rights}
Information on rights held in and over the resource.

\paragraph{Available}
Availability of data or model.

\paragraph{Format}
Form of model or data (file extension).

\paragraph{Reference}

\paragraph{Language}
Language of the resource.

\paragraph{Software}
Program in which the model has been implemented.

\paragraph{LanguageWrittenIn}
Language used to write the model, e.g. R or Matlab.

\paragraph{ModelCategory}

\paragraph{Status}
Curation status of the model.

\paragraph{Objective}
Objective of the model or data.

\paragraph{Description}
General description of the study, data or model.

\section{Scope}

\starttable
\R Product | Product | 0 | *
\R Hazard | \classlink{Hazard} | 0 | *
\R PopulationGroup | \classlink{PopulationGroup} | 0 | *
\R GeneralComment | string | 0 | 1
\R TemporalInformation | string | 0 || 1
\R SpatialInformation | \classlink{SpatialInformation} | 0 | 1
\stoptable

\subsection{Product}
\starttable
    \R Name | string | 1 | 1
    \R Description | string | 0 | 1
    \R Unit | string | 0 | 1
    \R Method | string | 0 | 1
    \R Packaging | string | 0 | 1
    \R Treatment | string | 0 | 1
    \R OriginCountry | string | 0 | 1
    \R OriginArea | string | 0 | 1
    \R FisheriesArea | string | 0 | 1
    \R ProductionDate | date | 0 | 1
    \R ExpiryDate | date | 0 | 1
\stoptable

\paragraph{Name}
The product-matrix (animal, food product, matrix, lab media, etc.) for which the model or data applies

\paragraph{Description}
Description of the product-matrix (animal, food product, matrix, lab media, etc.) for which the model or data applies

\paragraph{Unit}
Units of the product-matrix for which the model or data applies

\paragraph{Method}
Type of production for the product/ matrix

\paragraph{Packaging}
Describe container or wrapper that holds the product/matrix. Common type of packaging: paper or plastic bags, boxes, tinplate or aluminium cans, plastic trays, plastic bottles, glass bottles or jars.

\paragraph{Treatment}
Used to characterise a product/matrix based on the treatment or processes applied to the product or any indexed ingredient.

\paragraph{OriginCountry}
Country of origin of the food/product (ISO 3166-1-alpha-2 country code).

\paragraph{OriginArea}
Area of origin of the food/product (Nomenclature of territorial units for statistics – NUTS – coding system valid only for EEA and Switzerland).

\paragraph{FisheriesArea}
Fisheries or aquaculture area specifying the origin of the sample (FAO Fisheries areas).

\paragraph{ProductionDate}
date of production of food/product

\paragraph{ExpiryDate}
date of expiry of food/product

\section{DataBackground}

\starttable
    \R Study | \classlink{Study} | 0 | 1
    \R StudySample | \classlink{StudySample} | 0 | *
    \R DietaryAssessmentMethod | DietaryAssessmentMethod | 0 | *
    \R Laboratory | \classlink{Laboratory} | 0 | *
    \R Assay | \classlink{Assay} | 0 | *
\stoptable

\subsection{DietaryAssessmentMethod}

\starttable
    \R CollectionTool | string | 0 | 1
    \R NumberOfNonConsecutiveOneDay | string | 0 | 1
    \R SoftwareTool | string | 0 | 1
    \R NumberOfFoodItems | string | 0 | 1
    \R RecordTypes | string | 0 | 1
    \R FoodDescriptors | string | 0 | 1
\stoptable

\paragraph{CollectionTool}
food diaries, interview, 24-hour recall interview, food propensy questionnaire, portion size measurement aids, eating outside questionnaire

\paragraph{RecordTypes}
consumption occasion, mean of consumption, quantified and described as eaten, recipes for self-made

\paragraph{FoodDescriptors}
use foodex2 facets

\section{ModelMath}

\starttable
    \R Parameter | \classlink{Parameter} | 1 | *
    \R QualityMeasures | \classlink{QualityMeasures} | 0 | 1
    \R ModelEquation | \classlink{ModelEquation} | 0 | 1
    \R FittingProcedure | string | 0 | 1
    \R Exposure | \classlink{Exposure} | 0  | 1
    \R Event | string | 0 | 1
\stoptable

\chapter{DoseResponseModel}

\section{GeneralInformation}

\starttable
    \R ModelName | string | 1 | 1
    \R Source | string | 0 | 1
    \R Identifier | string | 0 | 1
    \R Author | \classlink{Contact} | 0 | *
    \R Creator | \classlink{Contact} | 1 | *
    \R CreationDate | date | 1 | 1
    \R ModificationDate | date | 0 | *
    \R Rights | string | 1 | 1
    \R Available | boolean | 0 | 1
    \R Format | string | 0 | 1
    \R Reference | \classlink{Reference} | 0 | *
    \R Language | string | 0 | 1
    \R Software | string | 0 | 1
    \R LanguageWrittenIn | string | 1 | 1
    \R ModelCategory | \classlink{ModelCategory} | 0 | 1
    \R Status | string | 0 | 1
    \R Objective | string | 0 | 1
    \R Description | string | 0 | 1
\stoptable

\paragraph{ModelName}
Name given to the model.

\paragraph{Source}
Related resource from which the described resource is derived.

\paragraph{Identifier}
Unambiguous ID given to the model.

\paragraph{Author}
Person who generated the model code originally.

\paragraph{Creator}
Person or institution who contributed to the encoding of the model in its present form by creating the model file.

\paragraph{CreationDate}
Temporal information on the model creation date.

\paragraph{ModificationDate}
Temporal information on the last modification of the model.

\paragraph{Rights}
Information on rights held in an over the resource.

\paragraph{Available}
Availability of model.

\paragraph{Format}
Form of the model (file extension).

\paragraph{Language}
Language of the resource (some data or reports can be available in French language for example).

\paragraph{Software}
Program in which the model has been implemented.

\paragraph{LanguageWrittenIn}
Language used to write the model, e.g. R or MatLab

\paragraph{Status}
Curation status of the model.

\paragraph{Objective}
Objective of the model.

\paragraph{Description}
General description of the model.

\section{Scope}

\starttable
    \R Hazard | string | 1 | *
    \R PopulationGroup | \classlink{PopulationGroup} | 0 | *
    \R GeneralComment | string | 0 | 1
    \R TemporalInformation | string | 0 | 1
    \R SpatialInformation | \classlink{SpatialInformation} | 0 | 1
\stoptable

\section{DataBackground}

\starttable
    \R Study | \classlink{Study} | 1 | 1
    \R StudySample | \classlink{StudySample} | 0  | *
    \R Laboratory | \classlink{Laboratory} | 0 | *
    \R Assay | \classlink{Assay} | 0 | *
\stoptable

\section{ModelMath}

\starttable
    \R Parameter | \classlink{Parameter} | 1 | *
    \R QualityMeasures | \classlink{QualityMeasures} | 0 | 1
    \R ModelEquation | \classlink{ModelEquation} | 0 | 1
    \R FittingProcedure | string | 0 | 1
    \R Exposure | \classlink{Exposure} | 0 | 1
    \R Event | string | 0 | 1
\stoptable

\appendix

\chapter{Examples}

\section{GenericModel}

\begin{lstlisting}[language=RAKIP, caption={Example of StudySample}]
<?xml version="1.0" encoding="UTF-8" ?>
<Document xmlns="http://www.example.org/GenericModel1.0.3">
    <GenericModel xmlns="http://www.example.org/GenericModel1.0.3">
        <GeneralInformation>
            <Name>Toy Model for Testing Purposes</Name>
            <Source>
                UNPUBLISHED STUDIES (EXPERIMENTS-OBSERVATIONS): Studies
                and surveys
            </Source>
            <Identifier>Toy_Model_Generic_01</Identifier>
            <Author>
                <Title>Dr.</Title>
                <FamilyName>Romanov</FamilyName>
                <GivenName>Natalia</GivenName>
                <Email>black_widow@marvel.com</Email>
                <Telephone>030 12345</Telephone>
                <StreetAddress>Nahmitzer Damm 40</StreetAddress>
                <Country>Russian Federation</Country>
                <City>Berlin</City>
                <Region>Berlin-Brandenburg</Region>
                <Organization>SHIELD</Organization>
            </Author>
            <Creator>
                <Title>Dr.</Title>
                <FamilyName>Romanov</FamilyName>
                <GivenName>Natalia</GivenName>
                <Email>black_widow@marvel.com</Email>
                <Telephone>030 12345</Telephone>
                <StreetAddress>Nahmitzer Damm 40</StreetAddress>
                <Country>Russian Federation</Country>
                <City>Berlin</City>
                <Region>Berlin-Brandenburg</Region>
                <Organization>SHIELD</Organization>
            </Creator>
            <Creator>
                <Title>Mr.</Title>
                <FamilyName>Parker</FamilyName>
                <GivenName>Peter</GivenName>
                <Email>peter@parker.com</Email>
                <Telephone>03301 1369158</Telephone>
                <StreetAddress>Am Kleinen Wannsee 16</StreetAddress>
                <Country>United States</Country>
                <City>Potsdam</City>
                <Region>Brandenburg</Region>
                <Organization>Parker Industries</Organization>
            </Creator>
            <CreationDate>2018-04-20</CreationDate>
            <Rights>Creative Commons Attribution-NonCommercial 4.0</Rights>
            <Format>.fskx</Format>
            <Reference>
                <IsReferenceDescription>true</IsReferenceDescription>
                <Type>PAMP</Type>
                <Date>3805-07-02</Date>
                <Doi>10.1111/risa.12758</Doi>
                <AuthorList>Jack Bauer, Kiefer Sutherland</AuthorList>
                <Title>Quantitative Risk Assessment of Norovirus Transmission
                    in Food Establishments: Evaluating the Impact of
                    Intervention Strategies and Food Employee Behavior on the
                    Risk Associated with Norovirus in Foods
                </Title>
                <Abstract>
                    This research looks at the work of Margaret C. Anderson,
                    the editor of the Little Review. The review published first
                    works by Sherwood Anderson, James Joyce, Wyndham Lewis,
                    and Ezra Pound. This research draws upon mostly primary
                    sources including memoirs, published letters, and a
                    complete collection of the Little Review. Most prior research
                    on Anderson focuses on her connection to the famous writers
                    and personalities that she published and associated with.
                    This focus undermines her role as the dominant creative force
                    behind one of the most influential little magazines published
                    in the 20th Century. This case example shows how little
                    magazine publishing is arguably a literary art.
                </Abstract>
                <Status>Accepted</Status>
                <Website>https://nature.com</Website>
                <Comment>publisher demands edits</Comment>
            </Reference>
            <Reference>
                <IsReferenceDescription>true</IsReferenceDescription>
                <Date>3805-07-07</Date>
                <Doi>10.1002/jmv.21237</Doi>
                <AuthorList>James Bond, Timothy Dalton</AuthorList>
                <Title>Norwalk virus: How infectious is it?</Title>
                <Abstract>This project involves discovering how the American
                    Revolution was remembered during the nineteenth century.
                    The goal is to show that the American Revolution was
                    memorialized by the actions of the United States government
                    during the 1800s. This has been done by examining events
                    such as the Supreme Court cases of John Marshall and the
                    Nullification Crisis. Upon examination of these events, it
                    becomes clear that John Marshall and John Calhoun (creator
                    of the Doctrine of Nullification) attempted to use the
                    American Revolution to bolster their claims by citing
                    speeches from Founding Fathers. Through showing that the
                    American Revolution lives on in memory, this research
                    highlights the importance of the revolution in shaping the
                    actions of the United States government.
                </Abstract>
                <Status>Legal</Status>
                <Website>www.sciencemag.org</Website>
                <Comment>Publisher hates lettuce.</Comment>
            </Reference>
            <Reference>
                <IsReferenceDescription>true</IsReferenceDescription>
                <Type>DICT</Type>
                <Date>3805-07-08</Date>
                <Doi>10.1111/j.1539-6924.1999.tb01143.x</Doi>
                <Title>Dose Response Models For Infectious Gastroenteritis</Title>
                <Abstract>The purpose of this research is to identify a subtype of
                    autism called Developmental Verbal Dyspraxia (DVD). DVD is a
                    motor-speech problem, disabling oral-motor movements needed
                    for speaking. The first phase of the project involves a
                    screening interview where we identify DVD and Non-DVD kids. We
                    also use home videos to validate answers on the screening
                    interview. The final phase involves home visits where we use
                    several assessments to confirm the child's diagnosis and
                    examine the connection between manual and oral motor
                    challenges. By identifying DVD as a subtype of Autism, we will
                    eliminate the assumption that all Autistics have the same
                    characteristics. This will allow for more individual
                    consideration of Autistic people and may direct future
                    research on the genetic factors in autism.
                </Abstract>
                <Status>Peer reviewed</Status>
                <Website>http://www.techbriefs.com</Website>
                <Comment>nerds</Comment>
            </Reference>
            <Language>English</Language>
            <Software>R</Software>
            <LanguageWrittenIn>R 3</LanguageWrittenIn>
            <ModelCategory>
                <ModelClass>Dose-response model</ModelClass>
                <ModelClassComment>
                    This Model Class is very special
                </ModelClassComment>
            </ModelCategory>
            <Status>Uncurated</Status>
            <Objective>Development of a dose-response models for Norwalk virus/
                norovirus</Objective>
            <Description>A norovirus dose response model is important for
                understanding its transmission and essential for development of a
                quantitative risk model. A new variant of the hit theory model of
                microbial infection was developed to estimate the variation in
                Norwalk virus infectivity, as well as the degree of virus aggregation,
                consistent with independent (electron microscopic) observations.
                Explicit modeling of viral aggregation was used to express virus
                infectivity per single infectious unit (particle). The hit theory
                model considers microbial infection as the result of a chain of
                conditional events: ingestion of one or more organisms from a
                Poisson-distributed suspension, followed by successful passage through
                any number of defensive barriers that may be present in the host.
                Individual organisms are thought to act independently, and any single
                surviving organism may reach an appropriate host cell and cause
                infection. Heterogeneity in the probability of individual organisms to
                achieve infection is modeled as a beta distribution. Illness is an
                important endpoint for risk assessment, especially for disease burden
                calculations. As illness is conditional on infection
                [Teunis et al.,1999], we wanted to study the probability of illness in
                infected subjects as a function of the applied dose. We used an
                existing model for illness dose response that is based on the concept
                of illness hazard during infection [Teunis et al., 1999].
            </Description>
        </GeneralInformation>

        <Scope>
            <Product>
                <Name>Lettuce</Name>
                <Description>fresh German lettuce</Description>
                <Unit>g</Unit>
                <Method>Organice production</Method>
                <Packaging>Packed</Packaging>
                <Treatment>Freezing</Treatment>
                <OriginCountry>Germany</OriginCountry>
                <OriginArea>Aachen, Kreisfreie Stadt</OriginArea>
                <FisheriesArea>Arctic Sea</FisheriesArea>
                <ProductionDate>3911-10-30</ProductionDate>
                <ExpiryDate>3911-12-01</ExpiryDate>
            </Product>
            <Product>
                <Name>Tomatoes</Name>
                <Description>not so fresh</Description>
                <Unit>g</Unit>
                <Method>Genetically modified</Method>
                <Packaging>Cardboard - paperboard</Packaging>
                <Treatment>Heating</Treatment>
                <OriginCountry>Spain</OriginCountry>
                <OriginArea>Lazio</OriginArea>
                <FisheriesArea>Mediterranean and Black Sea</FisheriesArea>
                <ProductionDate>3912-12-03</ProductionDate>
                <ExpiryDate>3913-02-01</ExpiryDate>
            </Product>
            <Product>
                <Name>
                    "Meat, preparations of meat, offals, blood, animal fats;
                    fresh, chilled or frozen, salted, in brine, dried or
                    smoked or processed as flours or meals; other processed
                    products such as sausages and food preparations based on
                    these
                </Name>
                <Description>
                    Pretty much any processed meat product imaginable
                </Description>
                <Unit>g</Unit>
                <Method>Farmed domestic or cultivated</Method>
                <Packaging>Vacuum package</Packaging>
                <Treatment>Fermentation</Treatment>
                <OriginCountry>United Kingdom</OriginCountry>
                <OriginArea>East Anglia</OriginArea>
                <FisheriesArea>Atlantic Ocean</FisheriesArea>
                <ProductionDate>3913-05-01</ProductionDate>
                <ExpiryDate>3914-05-01</ExpiryDate>
            </Product>
            <Hazard>
                <Type>Organic contaminants</Type>
                <Name>Norovirus (Norwalk-like virus)</Name>
                <Description>
                    norovirus is described as nast and hard to get rid of
                </Description>
                <Unit>CFU</Unit>
                <AdverseEffect>morbitity</AdverseEffect>
                <SourceOfContamination>sewage</SourceOfContamination>
                <MaximumResidueLimit>0.01 mg/kg</MaximumResidueLimit>
                <NoObservedAdverseAffectLevel>
                    10 mg
                </NoObservedAdverseAffectLevel>
                <LowestObservedAdverseAffectLevel>
                    40 mg
                </LowestObservedAdverseAffectLevel>
                <AcceptableOperatorExposureLevel>
                    50 mg
                </AcceptableOperatorExposureLevel>
                <AcuteReferenceDose>80 mg</AcuteReferenceDose>
                <AcceptableDailyIntake>20 mg</AcceptableDailyIntake>
            </Hazard>
            <Hazard>
                <Type>Microorganisms</Type>
                <Name>Salmonella Daarle</Name>
                <Description>
                    we dont know how that got into the tomatoes but it is there
                </Description>
                <Unit>Fill</Unit>
                <AdverseEffect>mortality</AdverseEffect>
                <SourceOfContamination>air</SourceOfContamination>
                <MaximumResidueLimit>0.11 mg/kg</MaximumResidueLimit>
                <NoObservedAdverseAffectLevel>
                    5 mg
                </NoObservedAdverseAffectLevel>
                <LowestObservedAdverseAffectLevel>
                    50 mg
                </LowestObservedAdverseAffectLevel>
                <AcceptableOperatorExposureLevel>
                    80 mg
                </AcceptableOperatorExposureLevel>
                <AcuteReferenceDose>100 mg</AcuteReferenceDose>
                <AcceptableDailyIntake>30 mg</AcceptableDailyIntake>
            </Hazard>
            <Hazard>
                <Type>Food additives</Type>
                <Name>Monoammonium glutamate</Name>
                <Description>tastes great but bad for your beach bod</Description>
                <Unit>fg/mL</Unit>
                <AdverseEffect>obesity</AdverseEffect>
                <SourceOfContamination>rodents</SourceOfContamination>
                <BenchmarkDose>123.12</BenchmarkDose>
                <MaximumResidueLimit>
                    0.25 - 0.4 mg/kg
                </MaximumResidueLimit>
                <NoObservedAdverseAffectLevel>
                    1 mg
                </NoObservedAdverseAffectLevel>
                <LowestObservedAdverseAffectLevel>
                    100 mg
                </LowestObservedAdverseAffectLevel>
                <AcceptableOperatorExposureLevel>
                    120 mg
                </AcceptableOperatorExposureLevel>
                <AcuteReferenceDose>140 mg</AcuteReferenceDose>
                <AcceptableDailyIntake>90 mg</AcceptableDailyIntake>
            </Hazard>
            <PopulationGroup>
                <Name>human consumer, no age specification</Name>
                <TargetPopulation>seniors</TargetPopulation>
                <PopulationDescription>
                    80% are considered susceptible to infection
                </PopulationDescription>
                <PopulationGender>50% male</PopulationGender>
                <BMI>18.5 - 24.9</BMI>
                <SpecialDietGroups>love cake</SpecialDietGroups>
                <Region>Madrid</Region>
                <Country>Spain</Country>
                <PopulationRiskFactor>
                    low physical activity
                </PopulationRiskFactor>
                <Season>spring</Season>
            </PopulationGroup>
            <PopulationGroup>
                <Name>human consumer, adult</Name>
                <TargetPopulation>soldiers</TargetPopulation>
                <PopulationDescription>highly vaccinated</PopulationDescription>
                <PopulationGender>90% male</PopulationGender>
                <BMI>18.5 - 24.9</BMI>
                <SpecialDietGroups>20% muslim</SpecialDietGroups>
                <Region>Mittelburgenland</Region>
                <Country>Austria</Country>
                <PopulationRiskFactor>bullet to the head</PopulationRiskFactor>
                <Season>summer</Season>
            </PopulationGroup>
            <PopulationGroup>
                <Name>human consumer, men</Name>
                <TargetPopulation>millenials</TargetPopulation>
                <PopulationDescription>
                    they get sick all the time
                </PopulationDescription>
                <PopulationGender>100% male</PopulationGender>
                <BMI>18.5 -24.9</BMI>
                <SpecialDietGroups>30% vegetarians</SpecialDietGroups>
                <Region>Nottingham</Region>
                <Country>United Kingdom</Country>
                <PopulationRiskFactor>vaping</PopulationRiskFactor>
                <Season>winter</Season>
            </PopulationGroup>
            <GeneralComment>
                (General Comment) The Scope of this model is universal
            </GeneralComment>
            <TemporalInformation>1900 - 2000</TemporalInformation>
        </Scope>
        <DataBackground>
            <Study>
                <Identifier>Study_Generic_Sheet_1</Identifier>
                <Title>Quantitative Risk Assessment of Norovirus Transmission
                    in Food Establishments: Evaluating the Impact of
                    Intervention Strategies and Food Employee Behavior on the
                    Risk Associated with Norovirus in Foods
                </Title>
                <Description>
                    This Study will show, wether the FSK Lab will correctly
                    read and run a generic and fully annotated model.
                </Description>
                <DesignType>Trial and Error</DesignType>
                <AssayMeasurementType>
                    It works or it doesn't
                </AssayMeasurementType>
                <AssayTechnologyType>
                    Anatomic-pathologic Tests
                </AssayTechnologyType>
                <AssayTechnologyPlatform>
                    Orbital Platform
                </AssayTechnologyPlatform>
                <AccreditationProcedureForTheAssayTechnology>ISO/IEC17025
                </AccreditationProcedureForTheAssayTechnology>
                <ProtocolName>Extraction Protocol of FSK</ProtocolName>
                <ProtocolType>Extraction Protocol</ProtocolType>
                <ProtocolDescription>The protocol is definitely not made up
                </ProtocolDescription>
                <ProtocolURI>
                    https://url-for-study-protocol-location.bfr.bund.de
                </ProtocolURI>
                <ProtocolVersion>version 1.0</ProtocolVersion>
                <ProtocolParametersName>Parameter 1</ProtocolParametersName>
                <ProtocolComponentsName>windows pc</ProtocolComponentsName>
                <ProtocolComponentsType>hardware</ProtocolComponentsType>
            </Study>
            <StudySample>
                <SampleName>Sample 1</SampleName>
                <ProtocolOfSampleCollection>
                    SampleID_1
                </ProtocolOfSampleCollection>
                <SamplingStrategy>Convenient sampling</SamplingStrategy>
                <TypeOfSamplingProgram>Diet study</TypeOfSamplingProgram>
                <SamplingMethod>According to Reg 152/2009</SamplingMethod>
                <SamplingPlan>Random sampling</SamplingPlan>
                <SamplingWeight>
                    description of the method employed to compute sampling
                    weight (nonresponse-adjusted weight)
                </SamplingWeight>
                <SamplingSize>10000.0</SamplingSize>
                <LotSizeUnit>log10(CFU/25g)</LotSizeUnit>
                <SamplingPoint>Catering</SamplingPoint>
            </StudySample>
            <StudySample>
                <SampleName>Sample 2</SampleName>
                <ProtocolOfSampleCollection>
                    SampleID_2
                </ProtocolOfSampleCollection>
                <SamplingStrategy>Selective sampling</SamplingStrategy>
                <TypeOfSamplingProgram>Monitoring</TypeOfSamplingProgram>
                <SamplingMethod>According to Reg 333/2007</SamplingMethod>
                <SamplingPlan>Stratified sampling</SamplingPlan>
                <SamplingWeight>
                    description of the method employed to compute sampling
                    weight (nonresponse-adjusted weight)
                </SamplingWeight>
                <SamplingSize>1000.0</SamplingSize>
                <LotSizeUnit>mL/kg</LotSizeUnit>
                <SamplingPoint>Air transport</SamplingPoint>
            </StudySample>
            <StudySample>
                <SampleName>Sample 3</SampleName>
                <ProtocolOfSampleCollection>SampleID_3
                </ProtocolOfSampleCollection>
                <SamplingStrategy>Census</SamplingStrategy>
                <TypeOfSamplingProgram>Control and eradication programmes
                </TypeOfSamplingProgram>
                <SamplingPlan>Multi-stage random sampling</SamplingPlan>
                <SamplingWeight>
                    description of the method employed to compute sampling
                    weight (nonresponse-adjusted weight)
                </SamplingWeight>
                <SamplingSize>2000.0</SamplingSize>
                <LotSizeUnit>mL/kg</LotSizeUnit>
                <SamplingPoint>Household</SamplingPoint>
            </StudySample>
            <DietaryAssessmentMethod>
                <CollectionTool>Food diaries</CollectionTool>
                <NumberOfNonConsecutiveOneDay>
                    5
                </NumberOfNonConsecutiveOneDay>
                <SoftwareTool>FoodWorks</SoftwareTool>
                <RecordTypes>Mean of consumption</RecordTypes>
                <FoodDescriptors>(Beet) Sugar</FoodDescriptors>
            </DietaryAssessmentMethod>
            <DietaryAssessmentMethod>
                <CollectionTool>Other observational studies</CollectionTool>
                <NumberOfNonConsecutiveOneDay>
                    10
                </NumberOfNonConsecutiveOneDay>
                <SoftwareTool>Nutritics</SoftwareTool>
                <RecordTypes>Quantified and described as eaten</RecordTypes>
                <FoodDescriptors>(Beet) Sugar</FoodDescriptors>
            </DietaryAssessmentMethod>
            <DietaryAssessmentMethod>
                <CollectionTool>Portion size measurement aids
                </CollectionTool>
                <NumberOfNonConsecutiveOneDay>20
                </NumberOfNonConsecutiveOneDay>
                <SoftwareTool>Purefood</SoftwareTool>
                <RecordTypes>Recipes for self-made</RecordTypes>
                <FoodDescriptors>(Beet) Sugar</FoodDescriptors>
            </DietaryAssessmentMethod>
            <Laboratory>
                <Accreditation>Accredited</Accreditation>
                <Name>National High Magnetic Field Laboratory</Name>
                <Country>United States</Country>
            </Laboratory>
            <Laboratory>
                <Accreditation>Everest Medical Laboratory</Accreditation>
                <Name>Everest Medical Laboratory</Name>
                <Country>India</Country>
            </Laboratory>
            <Assay>
                <Name>Bradford protein assay</Name>
                <Description>spectroscopic analytical procedure used to
                    measure the concentration of protein in a solution. It is
                    subjective, i.e., dependent on the amino acid composition
                    of the measured protein
                </Description>
                <DetectionLimit>30-300</DetectionLimit>
                <QuantificationLimit>5000 - 8000</QuantificationLimit>
                <ContaminationRange>500-4000</ContaminationRange>
            </Assay>
            <Assay>
                <Name>ELISA</Name>
                <Description>ELISA is a popular format of \"wet-lab\" type
                    analytic biochemistry assay that uses a solid-phase
                    enzyme immunoassay (EIA) to detect the presence of a
                    substance, usually an antigen, in a liquid sample or wet
                    sample.
                </Description>
                <ContaminationRange>200-800</ContaminationRange>
            </Assay>
            <Assay>
                <Name>Plaque-Assay</Name>
                <Description>standard method used to determine virus
                    concentration in terms of infectious dose. Viral plaque
                    assays determine the number of plaque forming units (pfu)
                    in a virus sample, which is one measure of virus quantity.
                </Description>
                <ContaminationRange>0.5 - 400</ContaminationRange>
            </Assay>
        </DataBackground>
        <ModelMath>
            <Parameter>
                <Id>Dose_matrix</Id>
                <Classification>input</Classification>
                <Name>Dose_matrix</Name>
                <Description>matrix with GEC NoV for each serving
                    (rows=servings; columns = number of different
                    employee-teams that prepare food)
                </Description>
                <Unit>Others</Unit>
                <UnitCategory>Other</UnitCategory>
                <DataType>matrixOfNumbers</DataType>
                <Source>Article</Source>
                <Subject>Animal</Subject>
                <Distribution>Bernoulli 1</Distribution>
                <Value>as.matrix(read.table(file =\"Dose_matrix.csv\",
                    sep=\",\", header = TRUE, row.names=1))</Value>
                <VariabilitySubject>days</VariabilitySubject>
                <MinValue>10000.0</MinValue>
                <MaxValue>0.0</MaxValue>
                <Error>0.5</Error>
            </Parameter>
            <Parameter>
                <Id>nInf</Id>
                <Classification>output</Classification>
                <Name>nInf</Name>
                <Description>number of infected individuals, mean over stores
                (2000 servings per store)</Description>
                <Unit>Others</Unit>
                <UnitCategory>Other</UnitCategory>
                <DataType>double</DataType>
                <Source>Model result</Source>
                <Subject>Batch of animals</Subject>
                <Distribution>Log-Logistic 2</Distribution>
                <VariabilitySubject>hours</VariabilitySubject>
                <MinValue>20000.0</MinValue>
                <MaxValue>0.1</MaxValue>
                <Error>0.4</Error>
            </Parameter>
            <Parameter>
                <Id>NIll</Id>
                <Classification>output</Classification>
                <Name>NIll</Name>
                <Description>number of ill individuals, mean over stores
                    (2000 servings per store)</Description>
                <Unit>Others</Unit>
                <UnitCategory>Others</UnitCategory>
                <DataType>double</DataType>
                <Source>Model result</Source>
                <Subject>Batch of products</Subject>
                <Distribution>Half Cauchy 1</Distribution>
                <MinValue>30000.0</MinValue>
                <MaxValue>0.3</MaxValue>
                <Error>0.3</Error>
            </Parameter>
            <Parameter>
                <Id>meanPos</Id>
                <Classification>output</Classification>
                <Name>prev18</Name>
                <Description>proportion of servings with >18 NoV</Description>
                <Unit>%</Unit>
                <UnitCategory>Arbitrary Fraction</UnitCategory>
                <DataType>double</DataType>
                <Source>Model result</Source>
                <Subject>Other</Subject>
                <Distribution>Binomial 1</Distribution>
                <VariabilitySubject>weight</VariabilitySubject>
                <MinValue>50000.0</MinValue>
                <MaxValue>0.2</MaxValue>
                <Error>0.1</Error>
            </Parameter>
            <Parameter>
                <Id>prev18</Id>
                <Classification>output</Classification>
                <Name>prev18</Name>
                <Description>proportion of servings with >18 NoV</Description>
                <Unit>%</Unit>
                <UnitCategory>Arbitrary Fraction</UnitCategory>
                <DataType>double</DataType>
                <Source>Model result</Source>
                <Subject>Other</Subject>
                <Distribution>Binomial 1</Distribution>
                <VariabilitySubject>weight</VariabilitySubject>
                <MinValue>50000.0</MinValue>
                <MaxValue>0.2</MaxValue>
                <Error>0.1</Error>
            </Parameter>
            <Parameter>
                <Id>prev100</Id>
                <Classification>output</Classification>
                <Name>prev100</Name>
                <Unit>%</Unit>
                <UnitCategory>Arbitrary Fraction</UnitCategory>
                <DataType>double</DataType>
                <Source>Model result</Source>
                <Subject>Feces</Subject>
                <Distribution>Discrete distribution</Distribution>
                <VariabilitySubject>color</VariabilitySubject>
                <MinValue>60000.0</MinValue>
                <MaxValue>0.12</MaxValue>
                <Error>0.01</Error>
            </Parameter>
            <Parameter>
                <Id>prev1000</Id>
                <Classification>output</Classification>
                <Name>prev1000</Name>
                <Description>proportion of servings with >1000 Nov</Description>
                <Unit>%</Unit>
                <UnitCategory>Arbitrary Fraction</UnitCategory>
                <DataType>double</DataType>
                <Source>Model result</Source>
                <Subject>Feces</Subject>
                <Distribution>Geometric 1</Distribution>
                <VariabilitySubject>shape</VariabilitySubject>
                <MinValue>70000.0</MinValue>
                <MaxValue>0.142</MaxValue>
                <Error>0.02</Error>
            </Parameter>
            <Parameter>
                <Id>alpha</Id>
                <Classification>input</Classification>
                <Name>alpha</Name>
                <Description>Alpha parameter in dose response model related
                    to probability of infection (shape of beta distribution)
                </Description>
                <Unit>Others</Unit>
                <UnitCategory>Other</UnitCategory>
                <DataType>double</DataType>
                <Source>Expert opinion</Source>
                <Subject>Carcass skin</Subject>
                <Distribution>Half-normal 1</Distribution>
                <Value>0.04</Value>
                <VariabilitySubject>age</VariabilitySubject>
                <MinValue>80000.0</MinValue>
                <MaxValue>0.01</MaxValue>
                <Error>0.03</Error>
            </Parameter>
            <Parameter>
                <Id>beta</Id>
                <Classification>input</Classification>
                <Name>beta</Name>
                <Description>Beta parameter in dose response model related to
                    probability of infection (scale of beta distribution)
                </Description>
                <Unit>Others</Unit>
                <UnitCategory>Other</UnitCategory>
                <DataType>double</DataType>
                <Source>Estimate</Source>
                <Subject>Product</Subject>
                <Distribution>Negative Binomial 1</Distribution>
                <Value>0.055</Value>
                <MinValue>900000.0</MinValue>
                <MaxValue>0.002</MaxValue>
                <Error>0.4</Error>
            </Parameter>
            <Parameter>
                <Id>eta</Id>
                <Classification>input</Classification>
                <Name>eta</Name>
                <Description>Eta parameter in dose response model related to
                    probability of illnes (scale parameter for gamma distribution)
                </Description>
                <Unit>Others</Unit>
                <UnitCategory>Other</UnitCategory>
                <DataType>double</DataType>
                <Source>Assumption</Source>
                <Subject>Package</Subject>
                <Distribution>Arcsine 2</Distribution>
                <Value>0.00255</Value>
                <VariabilitySubject>difficulty</VariabilitySubject>
                <MinValue>100000.0</MinValue>
                <MaxValue>0.01</MaxValue>
                <Error>0.5</Error>
            </Parameter>
            <Parameter>
                <Id>r</Id>
                <Classification>input</Classification>
                <Name>r</Name>
                <Description>
                    R parameter in dose response model related to probability
                    of illness (shape parameter for gamma distribution)
                </Description>
                <Unit>Others</Unit>
                <UnitCategory>Other</UnitCategory>
                <DataType>double</DataType>
                <Source>Not applicable</Source>
                <Subject>Belly</Subject>
                <Distribution>Multivariate Gaussian 2</Distribution>
                <Value>0.086</Value>
                <VariabilitySubject>species</VariabilitySubject>
                <MinValue>110000.0</MinValue>
                <MaxValue>0.1</MaxValue>
                <Error>0.05</Error>
            </Parameter>
            <QualityMeasures>
                <SSE>0.0</SSE>
                <MSE>0.2</MSE>
                <RMSE>0.3</RMSE>
                <RSquared>0.9</RSquared>
                <AIC>0.0</AIC>
                <BIC>1.0</BIC>
            </QualityMeasures>
        </ModelMath>
    </GenericModel>
</Document>    
\end{lstlisting}


\end{document}